\documentclass{my_cv}
\usepackage[margin=1in]{geometry}

\begin{document}

\name{Austin Goergen}

\contact
{goergena@oregonstate.edu}
{(541) 294-4052}
{3129 Main St. Apt. \#260, Philomath, OR 97370}

\vspace{-0.5em}

\begin{center}
\href{https://www.linkedin.com/in/austin-goergen-8370045198}{https://www.linkedin.com/in/austin-goergen-8370045198}
\end{center}

\section{Experience}

\datedsubsection{\textbf{Garmin AT} -- Salem, OR}{Mar. 2021--Sep. 2021}
\vspace{-0.75em}
Design Engineer Intern

\workitems
{Designed vital test equipment that is ~\$8,000 per unit cheaper than alternatives on the market}
{Organized and lead design reviews attended by mechanical, electrical, and process engineers}
{Successfully built proof of concept and created documentation for a novel proximity sensing method}

\datedsubsection{\textbf{Oregon State University Robotics Club}}{Nov. 2019--Present}
\vspace{-0.75em}
Mars Rover Electrical Engineering Lead

\vspace{-0.5em}
\begin{itemize}
    \item[-] Designing mixed-signal circuit boards using Altium Designer
    \vspace{-0.75em}
    
    \item[-] Coordinating with other OSURC Mars Rover sub-teams to design their required electronics
    \vspace{-0.75em}
    
    \item[-] Conducting design reviews of teammate's work to verify they meet established design standards
    \vspace{-0.75em}
\end{itemize}

\datedsubsection{\textbf{West Coast Contractors} -- Coos Bay, OR}{Summer 2019/2020}
\vspace{-0.75em}
Summer Intern
\vspace{-0.5em}
\begin{itemize}
    \item[-] Developed software to automate submittal assembly that reduced preparation time by 80\%
    \vspace{-0.75em}
    
    \item[-] Attended pre-bid meetings at potential jobs to collect information necessary for cost estimation
    \vspace{-0.75em}
    
    \item[-] Trained employees how to use a new cost-estimation software called eTakeoff
\end{itemize}

\section{Affiliations}

\datedsubsection{\textbf{IEEE-Eta Kappa Nu (IEEE-HKN)}}{Nov. 2019--Present}
\vspace{-0.75em}
President
\vspace{-0.5em}
\begin{itemize}
    \item[-] Providing tutoring to undergraduate electrical engineering students
    \vspace{-0.75em}
    
    \item[-] Organizing industry networking events for club members
    \vspace{-0.75em}
    
    \item[-] Promoting Eta Kappa Nu's tutoring services to undergraduate students
\end{itemize}

\datedsubsection{\textbf{Oregon State Drumline}}{Sep. 2018--Present}

\section{Education}
\datedsubsection{\textbf{Oregon State University}}{Expected Mar. 2023}
\vspace{-0.75em}
Bachelor of Science, Electrical and Computer Engineering \\
GPA: 3.94

\vspace{1em}
    \noindent\textbf{Relevant Coursework}
    
    \noindent\begin{tabular}{@{}l l l l l}
         Electrical Fundamentals & C/C++ & Data Structures & Digital Logic Design\\ 
         Electronics & Signals and Systems & Computer Networking &  Computer Organization
    \end{tabular}





\section{Skills}

\noindent\begin{tabular}{@{}l l l l l l}
     Altium Designer & Microcontrollers & FPGA & C/C++ & Python &  Assembly\\
    Linux & Git & MATLAB & Circuit Verification & SPICE & \LaTeX\\
\end{tabular}

\end{document} ​